Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
Pedogogic repeat of our argument that Pout is a model of Px so therefor the Posterior should be evaluated at Pout=Px.

Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$. For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one. Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for empirical inverse covariance weighting (left) and uniform weighting (right). Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$. After multiplying by the prior, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

>>>>

Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$. For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one. Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for empirical inverse covariance weighting (left) and uniform weighting (right). Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.  We invoke the Bayes interpretation and re-interpret as it as the posterior $P(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data and make a horizontal cut across at the data value $P_{\rm out} = P_{\rm x}$ to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
